### 2016-10-06 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Eds

temp <- dd

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col = 'darkgrey')+
  stat_smooth(method = 'lm',col='darkblue',fill = 'darkblue',formula = y~log(x),se = T)+
  annotate('text',x = 1,y = 2.9,label = 'A')

@@

temp <- subset(dd,Agemonths<12)
temp$LayYear <- factor(temp$LayYear)

Fig2 <- ggplot(temp,aes(x = LayYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_jitter(col = 'grey')+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0)

@@

>>>>

temp <- subset(dd,LayYear %in% c(2000:2008))

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL,col=factor(LayYear)))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  stat_smooth(method = 'lm',formula = y~log(x),se=F)
  annotate('text',x = 1,y = 2.9,label = 'A')

@@

temp <- subset(dd,LayYear>1995)

Fig2 <- ggplot(temp,aes(x = LayYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_boxplot(aes(group = LayYear),outlier.colour = 'grey',notch=F,alpha=0)+
  geom_smooth()

Fig2x <- ggplot(temp,aes(x = CatchYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_boxplot(aes(group = CatchYear),outlier.colour = 'grey',notch=F,alpha=0)+
  geom_smooth()

@@

temp <- dd
temp$LogAge <- log(temp$Agemonths)

m1 <- lm(RTL~LogAge,data=temp)
m2 <- lmer(RTL~LogAge+(1|CatchYear),data=temp)
m3 <- lmer(RTL~LogAge+(LogAge|CatchYear),data=temp)
m4 <- lmer(RTL~LogAge+(1|LayYear),data=temp)
m5 <- lmer(RTL~LogAge+(LogAge|LayYear),data=temp)

anova(m2,m3,m4,m5)
summary(m2)
summary(m3)
